\textbf{Multi-pitch estimation based on mathematical models}\\A pitch estimation framework and harmonic overtone sieve algorithm

### 2021-04-07 paper.tex
weer een stuk

\usepackage[english]{babel}
\usepackage[stretch=10, shrink=10]{microtype}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
% \usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{float}

@@

Pitch estimation can also be divided in a few subproblems. If a paper focusses on one of these subproblems, it also has to solve the other subproblems in order to test the system. Most papers do not publish their source code, which makes building upon other's work difficult, as often only the subproblem of interest is described. It also limits the research of the interaction between different solutions for the different subproblems. Because of this, we provide a framework in which can be built upon, as the implementation of a subproblem can easily be interchanged with another. The code can be found on "github.com/lucmans/dechord".

@@

Do note that this paper is a preliminary paper for a possible master thesis. The focus is on building a prototype which can perform monophonic AMT and presenting a first draft of a polyphonic version. Using this information, we will estimate if the thesis project is feasible.

@@

Another problem is choosing the real-time constraint for processing the input. Some papers claim 140 ms is sufficient~\cite{sloomboi}. This is however ridiculously long, as it would be more than a note difference when playing eight notes in 120 BPM. Also, as there is already a large latency due to how audio drivers work~\cite{os}. In practice, musicians often tweak their audio driver settings in order to gain 5 to 10 ms in latency, which makes the difference between being able to play faster pieces or not.

A big problem in polyphonic pitch estimation is the occurrence of overtones~\cite{oud}. As these overtones also have a periodic nature in the frequency domain, they can be detected using another Fourier transform~\cite{double}. This does however have a big impact on the latency, as performing a Fourier transform is computationally expensive.

@@

\section{Pitch estimation}
Automatic music transcription can be separated into two main problems; onset detection and pitch estimation~\cite{survey2}. In this paper, we will focus on pitch estimation. Because we always output the set of played notes for the last analysed frame, we do not require onset information. However, this information can improve the results of pitch estimation. For example, when a onset is detected, we can discard all samples from the transient.

As stated before, our goal is to perform the transcription in real-time. We choose a constraint of 6 ms. Most musicians work with a driver latency of 9 to 11 ms. On a good computer, this latency can be reduced to 3-5 ms. We will use these 6 ms of latency difference to perform our calculations in. Note that when playing more notes per second, latency becomes more of a problem. On slower pieces, we can get away with much larger latencies. In order to test this for yourself, we developed a tool which plays back the incoming audio signal with a user specifiable delay. This tool can be found under the "latency" branch in our GitHub.

@@

When using the Fourier transform, window functions have to by applied to the frames to prevent spectral leakage. Furthermore, the actual peak locations can be accurately interpolated using (Lagrangian) quadratic interpolation~\cite{interpol}. These concepts are further described in Section~\ref{sub:four}.

\subsection{Peak picking}
Peaks in the frequency domain correspond to predominant frequencies in the analysed frame. However, not every peak is of interest. Some peaks are generated by noise, especially in frequency ranges where there is no signal. These peaks can be filtered by requiring a minimal signal level to be considered a peak. Also, due to spectral leakage, peaks can be observed which are not in the original signal. Even though these peaks are minimized by using window functions, they still have to be taken into consideration. In polyphonic signals, harmonic overtones may slightly interfere (TODO: Maybe make preliminary section about overtone dissonance), which will also lead to inconsistent peaks.

On order to determine if a peak is significant enough, we calculate a Gaussian average envelope~\cite{gauss}. For every point in a frame, the Gaussian average is a weighted average of all points in the frame. The weight is determined by the distance from the current point. The distance in number of bins goes through a Gaussian function to determine the actual weight. Here, higher values for $\sigma$ make points close by weight more compared to distant points. How this envelope is precisely calculated and used for peak picking is described in Section~\ref{sec:impl}.

@@

To determine if notes are fundamentals or overtones, we use a "harmonic overtone sieve". Here, we look if any higher peak can be explained by the currently considered peak. The more other peaks a peak can explain, the more likely it is to be a fundamental. Moreover, if we can't explain some peaks based on the lowest peak, we know there was a second note in the source signal.

@@

The resolution of the Fourier transform is dependent on the number of samples in a frame. We sample the guitar signal at 192 kHz, which is the maximum sample rate for most audio interfaces. To allow guitarists to play mildly fast, we have to limit our frame length. If the frame size if too large, multiple separate notes may be included in one transform, which would make it seem like the notes were played at the same time. Moreover, frame sizes which are a power of two can be transformed more efficiently, which further restricts are frame size choice. We chose a frame size of 16584 samples, which at 192 kHz is 0.085 seconds (11.72 frames per second). This gives us a Fourier bin size of 11.72 Hz. At first glance, such a large bin size seems like a big problem, as the smallest interval that can be played on a guitar (G\#\textsubscript{2}-A\textsubscript{2}) is about 6 Hz. However, the overtones of these notes will have more Hz between them. Also, as discussed in Section~\ref{sec:future}, we might be able to increase the frame size without reducing our frame rate too much.

It is possible to determine the actual peak location within a Fourier bin using quadratic interpolation~\cite{interpol2}. The lobes in the frequency domain form parabolas in a dB (logarithmic) scale, which allows quadratic interpolation to be very accurate. This interpolation is performed during the peak picking step, so only peaks that matter are interpolated.

@@

\subsection{Peak picking}
Three different peak picking algorithms have been implemented. The first picks every local maximum (every \texttt{i} where \texttt{data[i - 1] < data[i] \&\& data[i] > data[i + 1]}). The other two algorithms pick peaks based on a Gaussian average envelope. One algorithm picks all peaks which are above this average and the other only picks the highest peak for each spectral lobe above this average. Using this envelope, we effectively filter small local maxima close to large local maxima.

The Gaussian average envelope is calculated by taking the weighted average of a configurable number of samples in a Fourier window. The weights are determined by a Gaussian function ($e^{-\pi(\frac{x}{\sigma})^2}$) where the mean is the point in the envelope which is calculated. The value of sigma can be changed in \texttt{config.h}. Higher values for $\sigma$ makes points around the mean have a higher weighting. We choose a value of 1.2, but this value could be optimized for better results.

@@

@@

Polyphonic note detection can use a algorithm similar to the monophonic algorithm. As the number of played notes in unknown in the polyphonic case, we have to determine if a note is a fundamental or overtone. We cannot just set a threshold for the number of overtones a fundamental should have, because the number of detected overtones is very inconsistent. To solve this, we present a harmonic overtone sieve algorithm. Instead of directly looking for fundamentals, we try to sieve away all harmonics until we are left with fundamentals. We start at the lowest peak end mark all its possible overtones. If there are still unmarked peaks left, they are likely from another note. We can repeat this process until no more peaks can be sieved.

@@

\subsection{UI}
TODO: User interface and user interaction description.

\subsection{Latency}
The latency of our system can be divided in two different latencies, the time to fill a frame with samples and frame processing time. Because our algorithm works on a "per frame" basis instead of a "per sample" basis, we have to wait until the audio driver has fetched enough samples for us to fill a frame. The time it takes to start analysing a frame after receiving the first sample of this frame can be calculated by dividing the number of samples per frame by the sample rate. This is equal to the length of a frame. However,

We use a frame size of 16384 samples and a sample rate of 192000 samples per second, which equates to a frame length of 85.3 ms. This is well over our real-time constraint. Unfortunately, we cannot change this value too much. The sample rate is already at the maximum of most audio interfaces. We also cannot lower the number of samples per frame while using the Fourier transform, as it would further reduce the frequency resolution. However, as will be explained in Section~\ref{sub:futlaten}, this might not be a problem, as we can greatly reduce this latency by employing multi-threading.

We can control the second kind of latency by optimizing our algorithms. In Section~\ref{sub:algspeed}, we will measure the processing time of the different algorithms.

\section{Experiments}  \label{sec:exp}
We will perform a few experiments to test our system. The used audio equipment has a large effect on the results and in turn effects what parameters work best for the system. During development, an electric guitar with active humbucker pickups was used. To convert the analog signal to a sampled digital signal, a Behringer UMC404HD was used. This audio interface has a dynamic range of 100 dB. Like most audio interfaces, this is much less than the dynamic range of a sample (144 dB for 24 bit integer). We opted not to amplify the signal in software, as it will distort it. Also, if amplification is not done carefully, the signal will peak, which means that peaks are cut off. The tests were performed on an AMD 3700X CPU.

Often used datasets for evaluating pitch estimation focus on different goals than this paper. For instance, they focus on transcribing multiple instruments at once or having instrument invariance. They also do not focus on real-time transcription, which makes the problem much harder. However, in order to present some comparative measure, we will use the Mirex dataset for "Multiple Fundamental Frequency Estimation \& Tracking"~\cite{data}. TODO: This dataset consists of actual songs.

We also constructed our own dataset to evaluate the performance. This dataset will be a more technical dataset containing scales and intervals played on a guitar. Scales allow us to measure the monophonic performance. As scales are easy to play, multiple recordings should have the same results. This allows us to isolate and measure other variables, such as the effect of tempo or playing the scale higher/lower. Recordings of different intervals allow us to measure the polyphonic performance. By measuring all two note intervals, we can identify any problems with specific intervals. As the distance in frequency in an interval increases when the same interval is played at higher notes, we record the intervals at multiple root notes. We will also measure the performance on the four basic triads: the major triad, minor triad, augmented triad and diminished triad.

\subsection{Latency}  \label{sub:algspeed}
The processing time of our system is very important, as it will directly impact the latency.

@@

\section{Future work}  \label{sec:future}
How to make results more consistent (onset detection, transient filtering). How to make the project more real-time (threading rolling transforms). Also deliberately detuning strings for better results. Amplification->more overtones detected but also more noise.

>>>>

\usepackage[english]{babel}
\usepackage[stretch=10, shrink=10]{microtype}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{float}

@@

Pitch estimation can be divided into a few subproblems. If a paper focusses on one of these subproblems, it also has to solve the other subproblems in order to test the system. Most papers do not publish their source code, which makes building upon other's work difficult. It also limits the research of the interaction between different solutions for the different subproblems. Because of this, we provide a framework in which can be built upon, as the implementation of a subproblem can easily be interchanged with another. The code can be found on "github.com/lucmans/dechord".

@@

Note that this paper is a preliminary paper for a possible master thesis. The focus is on building a prototype which can perform monophonic AMT and presenting a first draft of a polyphonic version. Using this information, we will estimate if the thesis project is feasible.

@@

A big problem in polyphonic pitch estimation is the occurrence of overtones~\cite{oud}. As these overtones also have a periodic nature in the frequency domain, they can be detected using another Fourier transform~\cite{double}. This does however have a big impact on the latency, as performing a Fourier transform is computationally expensive. Also, notes which are at octave intervals have the same periodicity~\cite{octave}, which makes them difficult to distinguish.

Another problem is choosing the real-time constraint for processing the input. Some papers claim 140 ms is sufficient~\cite{sloomboi}. This is however ridiculously long, as it would be about a note difference when playing eight notes in 200 BPM. Also, as there is already a large latency due to how audio drivers work~\cite{os}. In practice, musicians often tweak their audio driver settings in order to gain 5 to 10 ms in latency, which makes the difference between being able to play faster pieces or not.

@@

\section{Pitch estimation}
Automatic music transcription can be separated into two main problems; onset detection and pitch estimation~\cite{survey2}. In this paper, we will focus on pitch estimation. Because we always output the set of played notes for the last analysed frame, we do not require onset information. However, this information can improve the results of pitch estimation. For example, when an onset is detected, we can discard all samples from the transient.

As stated before, our goal is to perform the transcription in real-time. We choose a constraint of 6 ms. Most musicians work with a driver latency of 9 to 11 ms. On a good computer, this latency can be reduced to 3-5 ms. We will use these 6 ms of latency difference to perform our calculations in. Note that when playing more notes per second, latency becomes more of a problem. On slower pieces, we can get away with much larger latencies. In order to test this for yourself, we developed a tool which plays back the incoming audio signal with a user specifiable delay. This tool can be found under the "latency" branch in our GitHub repository.

@@

When using these transforms, window functions have to by applied to the frames to prevent spectral leakage. Furthermore, the actual peak locations can be accurately interpolated using (Lagrangian) quadratic interpolation~\cite{interpol}. These concepts are further described in Section~\ref{sub:four} and Section~\ref{sub:peak} respectively.

\subsection{Peak picking}
Peaks in the frequency domain correspond to predominant frequencies in the analysed frame. However, not every peak is of interest. Some peaks are generated by noise. Many of these peaks can be filtered by requiring a minimal signal level to be considered a peak. Furthermore, due to spectral leakage, peaks can be observed which are not in the original signal. This kind of noise can be minimized by choose a good window function~\cite{window}. In polyphonic signals, harmonic overtones may slightly interfere (TODO: Maybe make preliminary section about overtone dissonance), which will may lead to inconsistent and oscillating peaks.

On order to determine if a peak is significant enough, we first calculate a Gaussian average envelope~\cite{gauss}. For every point in a frame, the Gaussian average is a weighted average of all points in the frame. The weight is determined by the distance from the current point. The distance in number of bins goes through a Gaussian function to determine the actual weight. Here, higher values for $\sigma$ make points close by weight more compared to distant points. How this envelope is precisely calculated and used for peak picking is described in Section~\ref{sub:peak}.

@@

To determine if notes are fundamentals or overtones, we use a "harmonic overtone sieve". Here, we look if any higher peak can be explained by the currently considered peak. The more other peaks a peak can explain, the more likely it is to be a fundamental. Moreover, if we cannot explain a certain peak, it is likely that there is a second note in the source signal.

@@

The resolution of the Fourier transform is dependent on the number of samples in a frame. We sample the guitar signal at 192 kHz, which is the maximum sample rate for most audio interfaces. To allow guitarists to play mildly fast, we have to limit our frame length. If the frame size if too large, multiple separate notes may be included in one transform, which would make it seem like the notes were played at the same time. Moreover, frame sizes which are a power of two can be transformed more efficiently, which further restricts are frame size choice. We chose a frame size of $2^{14} = 16384$ samples, which at 192 kHz is 0.085 seconds (11.72 frames per second). This gives us a Fourier bin size of 11.72 Hz. At first glance, such a large bin size seems like a big problem, as the smallest interval that can be played on a guitar (G\#\textsubscript{2}-A\textsubscript{2}) is about 6 Hz. However, the overtones of these notes will have more Hz between them, which makes to possible to differentiate the two notes.% Also, as discussed in Section~\ref{sec:future}, we might be able to increase the frame size without reducing our frame rate too much.

@@

\subsection{Peak picking} \label{sub:peak}
Three different peak picking algorithms have been implemented. The first picks every local maximum (every \texttt{i} where \texttt{data[i - 1] < data[i] \&\& data[i] > data[i + 1]}). The other two algorithms pick peaks based on a Gaussian average envelope. One algorithm picks all peaks which are above this average and the other only picks the highest peak for each spectral lobe above this average. Using this envelope, we effectively filter small local maxima close to large local maxima.

The Gaussian average envelope is calculated for every Fourier bin $i$ by taking the weighted average of a arbitrary number of bins around $i$. The weights are determined by a Gaussian function ($e^{-\pi(\frac{x}{\sigma})^2}$). The value of sigma and number of bins around $i$ can be changed in \texttt{config.h}. Higher values for $\sigma$ makes points around the considered point have a higher weighting. We choose a value of 1.2, but this value could be optimized for better results.

@@

It is possible to determine the actual peak location within a Fourier bin using quadratic interpolation~\cite{interpol2}. Here, we calculate a value $p \in [-\frac{1}{2}, \frac{1}{2}]$, which is the location of the actual peak relative to the found peak in number of Fourier bins. In order to calculate $p$, we need the height of our found peak ($y(0)$) and the height of the two neighbouring bins ($y(-1)$ and $y(1)$). As quadratic interpolation is more accurate in the dB (logarithmic) scale, we define:
\begin{center}\vspace{-1mm}
    $\alpha = \log y(-1)$\\
    $\beta = \log y(0)$\\
    $\gamma = \log y(1)$
\end{center}\vspace{-1mm}
Then, we can calculate $p$ as follows:
\begin{center}\vspace{-1mm}
    $p = \frac{1}{2} \frac{\alpha - \gamma}{\alpha - 2\beta + \gamma}$
\end{center}\vspace{-1mm}
Given the Fourier bin size, we can calculate the frequency of the peak $i$ by multiplying the bin size by $i + p$.

@@

Polyphonic note detection can use a algorithm similar to the monophonic algorithm. As the number of played notes in unknown in the polyphonic case, we have to determine if a note is a fundamental or overtone. We cannot just set a threshold for the number of overtones a fundamental should have, because the number of detected overtones is very inconsistent. To solve this, we present a harmonic overtone sieve algorithm. Instead of directly looking for fundamentals, we try to sieve away all harmonics until we are left with fundamentals. We start at the lowest peak end mark all its possible overtones. If there are still unmarked peaks left, they are likely from another note and we sieve its overtones away. We can repeat this process until no more peaks can be sieved.

@@

\subsection{Latency}
The latency of our system can be divided in two different latencies, the time to fill a frame with samples and frame processing time. Because our algorithm works on a "per frame" basis instead of a "per sample" basis, we have to wait until the audio driver has fetched enough samples for us to fill a frame. The time it takes to start analysing a frame after receiving the first sample of this frame can be calculated by dividing the number of samples per frame by the sample rate. This is equal to the length of a frame. In practical terms, it is the maximum latency on detecting a newly played note. The average latency is obtained by dividing this number by two.

We use a frame size of 16384 samples and a sample rate of 192000 samples per second, which equates to a frame length of 85.3 ms. This is well over our real-time constraint. Unfortunately, we cannot change this value too much. The sample rate is already at the maximum of most audio interfaces. We also cannot lower the number of samples per frame while using the Fourier transform, as it would further reduce the frequency resolution. However, as will be explained in Section~\ref{sub:futlaten}, this might not be a problem, as we can reduce this latency by employing multi-threading.

We can control the second kind of latency by optimizing our algorithms. In Section~\ref{sec:exp}, we will measure the processing time of the different algorithms.

\section{Experiments}  \label{sec:exp}
We will perform a few experiments to test our system. The used audio equipment has a large effect on the results and in turn effects what parameters work best for the system. During development, an electric guitar with active EMC humbucker pickups was used. To convert the analog signal to a sampled digital signal, a Behringer UMC404HD was used. This audio interface has a dynamic range of 100 dB. Like most audio interfaces, this is much less than the dynamic range of a sample (144 dB for 24 bit integer). We opted not to amplify the signal in software, as it will distort it; especially if not done carefully. The tests were performed on an AMD 3700X CPU.

Often used datasets for evaluating pitch estimation focus on different goals than this paper. For instance, they focus on transcribing multiple instruments at once or having instrument invariance. They also do not focus on real-time transcription, which makes the problem much harder. However, in order to present some comparative measure, we will use the Mirex dataset for "Multiple Fundamental Frequency Estimation \& Tracking"~\cite{data}. TODO (when I receive it): Short description of dataset.

We also constructed our own dataset to evaluate the performance. This dataset will be a more technical dataset; consisting of scales and intervals played on a guitar. Scales allow us to measure the monophonic performance. As scales are easy to play, multiple recordings should have the same results. This allows us to isolate and measure other variables, such as the effect of tempo or playing the scale higher/lower. Recordings of different intervals allow us to measure the polyphonic performance. By measuring all two note intervals, we can identify any problems with specific intervals. As the distance in frequency in an interval increases when the same interval is played at higher notes, we record the intervals at multiple root notes. We will also measure the performance on the four basic triads: the major triad, minor triad, augmented triad and diminished triad.

Note that when repeating our experiments, your results may very slightly. This is because the results of the Fourier transform from FFTW are not consistent~\cite{fftw}. This is especially noticeable in inconsistent latencies.

\subsection{Monophonic performance: scales}
To test the monophonic performance of our system, we first measure the performance of scales at different pitch ranges. We expect the system to perform better at higher pitches, as the distance in frequency between is higher. The scales are played at a speed of two notes per second. This equates to playing fourth notes on 120 BPM. We play the scales at a relatively slow speed, such that this cannot become a limiting factor. The slower speed also helps to see if mistakes are the result of transients, as these mistakes should vanish as the note persists. We only play the C major scale, but change the starting note (mode). We play the full vertical scale according to this position~\cite{scale}. Each position has 17 notes, except for $\text{F}_2$, which has 18 notes. In Table~\ref{tab:monperf}, we summarize the results of the experiment. We denote the different starting positions as $n_\text{start}$. For every starting position, we denote the accuracy ($a$), the accuracy without transient errors ($a_\text{trans}$), the accuracy without octave errors $a_\text{oct}$ and the total accuracy without both of these errors ($a_\text{tot}$). The accuracy is calculated by dividing the number of correctly determined frames by the total number of frames with notes. The only frames without notes are positioned at the start and end of a file. We omitted these frames from the results, as they are always correctly determined to be empty frames.
\begin{table}[H]\vspace{-3mm}
    \centering
    \begin{tabular}{r|rrrr}
        $n_\text{start}$ & $a$ & $a_\text{trans}$ & $a_\text{oct}$ & $a_\text{tot}$ \\
        \hline
        $\text{E}_2$ & \% & \% & \% & \% \\
        $\text{F}_2$ & \% & \% & \% & \% \\
        $\text{G}_2$ & \% & \% & \% & \% \\
        $\text{A}_2$ & \% & \% & \% & \% \\
        $\text{B}_2$ & \% & \% & \% & \% \\
        $\text{C}_3$ & \% & \% & \% & \% \\
        $\text{D}_3$ & \% & \% & \% & \% \\
        $\text{E}_3$ & \% & \% & \% & \%
    \end{tabular}
    \caption{Accuracy of monophonic $f_0$ estimation on C major scale at two notes per second for different starting positions.}
    \label{tab:monperf}
\end{table}\vspace{-3mm}
As mentioned before, our system is not yet resilient against noise from transients. Also, solving the octave problem is outside the scope of this paper. Because of this, we also list the results ignoring these problems. TODO: reflect on results

\subsection{Polyphonic performance: intervals}
To test the polyphonic performance of our system, we let it determine the played notes in an interval. We will play every interval within an octave to test if there are any problems with separating the notes in specific intervals. For instance, some interference may cause oscillating peaks in the frequency domain. Again, we will try all the intervals at different root notes, as especially for intervals the pitch of the root note may make a big difference. Even though the overtones of low pitched notes in small intervals might make it possible to distinguish the individual notes, we might not detect enough overtones to actually do so. In Table~\ref{tab:polperf} is a summary of the results. Here, we list the number of semitones $n$ between the two notes in an interval, if both notes were correctly found (yes or no) and if there were other notes reported which were not transients.
\begin{table}[H]\vspace{-3mm}
    \centering
    \begin{tabular}{r|rr}
        $n$ & both & other \\
        \hline
        1  &  &  \\
        2  &  &  \\
        3  &  &  \\
        4  &  &  \\
        5  &  &  \\
        6  &  &  \\
        7  &  &  \\
        8  &  &  \\
        9  &  &  \\
        10 &  &  \\
        11 &  & 
    \end{tabular}
    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_2$.}
    \label{tab:polperf}
\end{table}\vspace{-3mm}
In the tables, we can see that... (not enough overtones for low pitched intervals...)

\subsection{Latency}  \label{sub:algspeed}
The processing time of our system is very important, as it will directly impact the latency. We will only measure the time between receiving a frame from the audio driver until the answer is computed, as the time spent waiting on enough samples is fully determined by the number of samples in a frame and the sampling rate. The total processing time and the processing time of the individual steps and the total system can be seen in Figure~\ref{fig:snel}.
\begin{figure}[H]%\vspace{-2mm}
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        % \includegraphics[width=\linewidth]{figures/circarea_low.png}
        \captionof*{figure}{Scales}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        % \includegraphics[width=\linewidth]{figures/circarea_high.png}
        \captionof*{figure}{Intervals}
    \end{subfigure}
    \caption{Processing time of the different algorithms}
    \label{fig:snel}
\end{figure}%\vspace{-4mm}
TODO: The results are what they are...

@@

\section{Future work}  \label{sec:future}
How to make results more consistent (onset detection, transient filtering). How to make the project more real-time (threading rolling transforms). Also deliberately detuning strings for better results. Amplification->more overtones detected but also more noise. Remove spikes in latency by saving FFTW wisdom.
